An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-22 neurips-19/poly-embed.tex
Adding paragraph on 0-1 loss example

\raf{How hinge fits in}
\jessie{Added the paragraph below.}
\raf{Give it another shot, but focus on flexing our formalism.  What does hinge elicit?  How can we see that it embeds (twice) 0-1 loss from our definitions?  Then maybe one sentence for why logistic does not.}
To illustrate the idea of embeddings, we now look in detail at two key examples.
First, consider a binary classification problem on the outcomes $\{-1, +1\}$.
Both the hinge loss $L_{hinge}(u,y) := (1 - uy)_+$ and logistic loss $L_{logistic}(u,y) := \ln\left(1 + \exp(-uy)\right)$ are convex surrogates that are minimized in expectation by predicting the mode, as is 0-1 loss $\ell_{mode}(r,y) := \Ind[r\neq y]$.
However, we say that hinge loss embeds the mode, while logistic loss does not.

To see this, $\inprod{p}{L_{logistic}(u)}$ has an infinite set of minimizers over $p \in \Delta_2$ that are mapped to two reports, $\pm 1$.
If the linked surrogate correctly minimizes $L$ in expectation, 
\jessie{Come back to flesh this out if space?}

>>>>

\raf{Give it another shot, but focus on flexing our formalism.  What does hinge elicit?  How can we see that it embeds (twice) 0-1 loss from our definitions?  Then maybe one sentence for why logistic does not.}
To illustrate the idea of embeddings, we now look in detail at two key examples.
First, consider a binary classification problem on the outcomes $\{-1, +1\}$.
Both the hinge loss $L_{hinge}(u,y) := (1 - uy)_+$ and logistic loss $L_{logistic}(u,y) := \ln\left(1 + \exp(-yu)\right)$ are convex surrogates that are minimized in expectation by predicting the mode, as is 0-1 loss $\ell_{0-1}(r,y) := \Ind[r\neq y]$.
However, we say that hinge loss embeds twice the 0-1 loss, while logistic loss does not embed 0-1 loss.
First, taking $\R = \{-1,1\}$ and the embedding to be the identity, we can write 
\begin{center}
\begin{tabular}{ll}
	$\inprod{p}{\ell_{0-1}(1)} = (1-p_1)$ & $\inprod{p}{\ell_{0-1}(-1)} = (p_1)$\\
	$\inprod{p}{L_{hinge}(1)} = 2(1-p_1)$ & $\inprod{p}{L_{hinge}(-1)} = 2(p_1)$
\end{tabular}
\end{center}

Thus, for every $r \in \R$ and $p \in \simplex$, we have $2 \inprod{p}{\ell_{0-1}(r)} = \inprod{p}{L_{hinge}(\varphi(r))}$.

Now to see that optimal reports map to optimal reports, consider that 
\[
\prop{2 \ell_{0-1}} = \begin{cases}
1 & p_1 > 1/2 \\
\{-1,1\} & p_1 = 1/2\\
-1 & p_1 < 1/2
\end{cases}
\quad
\prop{L_{hinge}} = \begin{cases}
1 & p_1 > 1/2 \\
[-1,1] & p_1 = 1/2\\
-1& p_1 < 1/2
\end{cases}
\]

One can see logistic loss does not embed $\ell_{0-1}$ because it elicits a continuous property, so there is an infinite set of unique optima over $\simplex$, and thus no injection exists mapping this set to $\{-1,1\}$.
